Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

            \item Denote by $r_i$ ($i \in [k-2]$) the full rectangle of $\bm{t}[i]$. 
            For any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.
        }

@@

@@

By statements (b) and (c) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, statement (a) of Lemma~\ref{lmm:hv:type1:properties} assures us that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.

>>>>

            \item Denote by $r_i$ ($i \in [k-2]$) the full rectangle of $\bm{t}[i]$. 
            For any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        }

@@

        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $\bm{t} = (r_1, r_2, ...,$ $r_{k-2})$ belongs to $\J(R_1', R'_2, ..., R'_{k-2})$, and       
        $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$.

@@

By statements (b) and (2) of Lemma~\ref{lmm:hv:type1:properties}, the set $\J^*$ thus computed indeed satisfies \eqref{eqn:hv:type1:J*}. Furthermore, if we are given $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ for each $\bm{t}$, statement (a) of Lemma~\ref{lmm:hv:type1:properties} assures us that the above algorithm runs in $O(1 + k \cdot |\J^*|) = O(1 + k \cdot \out)$ time.
